### 2021-04-28 manuscript.Rmd
+ Bayes naive effect size estimate for consistency - + n per look and cumulative n to all procedures

```{r setup, include = FALSE}
knitr::opts_chunk$set()
library(papaja)
library(tidyverse)
library(ggplot2)
library(grid)
library(rpact)
library(pracma)
library(coda)
library(BayesFactor)
library(parallel)
library(metafor)
library(beepr)
library(citr)

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set()
library(papaja)
library(tidyverse)
library(ggplot2)
library(grid)
library(rpact)
library(pracma)
library(coda)
library(BayesFactor)
library(parallel)
library(metafor)
library(citr)
